---
title: "Capstone EDA"
output: html_document
date: "2026-02-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup
# Import Libraries
```{r}
library(tidyverse)
```
# Import Data
```{r}
qal <- read_csv("QAL Performance for MSBA.csv")
```


## 1. Business Problem Statement

MasterControl’s Manufacturing Solutions product (Mx) is significantly underperforming its Quality Solutions product (Qx). The company believes it may not be targeting the right companies or the right people within those companies, leading to missed revenue opportunities and wasted marketing expenditures.

We have been given 16,644 qualified sales leads (QALs) from Jan 2024 to Dec 2025. These come from 15,371 unique contacts across 14 different variables. The goal with this binary classification problem is to identify which account and contact characteristics are the most predictive of lead progression.

The target variable is next_stage__c, which is the outcome of each qualified sales lead.
The binary outcome will be defined as follows:
- Success (1): The lead progressed to SQL, SQO, or Won.
- Failure (0): The lead was Recycled, Excluded, Lost, returned to MQL, or returned to INQ.

## 2. Questions to Guide Exploration
- What is the distribution of sales leads across industries? Does that differ between Mx and Qx?
- What industries have the highest conversion rates for Mx? Which are the lowest?
- Do the best / worst performing industries for Mx differ from Qx?
- Which manufacturing models show the highest Mx conversion rates? Which show the highest for Qx?
- Do companies that manufacture in-house convert better for Mx than those that are more service-oriented?
- Which products that are being manufactured convert the best for Mx?
- Does company size impact conversion rates? Is it different between Mx and Qx?
- Are there regional differences in convertion rates?
- What seniority levels are the most common? Which ones convert best for Mx vs Qx?
- Which functional areas (in job title) are the most common? Which ones convert best for Mx vs Qx?
- Are there any seniority / function combinations that perform better than others?
- Is there any difference in lead priority levels that show higher conversion rates?
- Which marketing channels produce the highest conversion rates?
- Are there certain channels that work better for Mx vs Qx?
- Have Mx conversion rates improved over time? Are there any seasonal patterns?
- Which account types convert well for both Mx and Qx (cross sell opportunities)?

## Inspect Data
```{r}
summary(qal)
str(qal)
dim(qal)

# Inspect raw data
head(qal)
tail(qal)

# Check column names
names(qal)

# Count missing values
colSums(is.na(qal))

# Count unique values per column
sapply(qal, n_distinct)
```

# Categorical Variable Distributions
```{r}
table(qal$solution_rollup)
table(qal$next_stage__c)
table(qal$`acct target industry`)
table(qal$`acct tier rollup`)
table(qal$`acct territory rollup`)
```
# Check for Duplicates
```{r}
# QAL IDs
sum(duplicated(qal$'QAL ID'))

# Contact IDs
n_distinct(qal$'contact/lead id')
```
## Data Cleaning
```{r}
# Filter out Ax leads
qal_clean <- qal |>
  filter(solution_rollup != "Ax") |>
  filter(!is.na(next_stage__c)) |>
  mutate(
    progressed = if_else(next_stage__c %in% c("SQL", "SQO", "Won"), 1L, 0L)
  )

# Check dimensions
dim(qal_clean)

# Check target variable distribution
table(qal_clean$progressed)

# Check conversion rate by product
qal_clean |>
  group_by(solution_rollup) |>
  summarise(
    n = n(),
    conversions = sum(progressed),
    conv_rate = mean(progressed)
  )
```
```{r}
# Handle 'Not Enough Info Found' as missing data in site function and manufacturing model.
qal_clean <- qal_clean |>
  mutate(
    `acct primary site function` = na_if(`acct primary site function`, "Not Enough Info Found"),
    `acct manufacturing model`   = na_if(`acct manufacturing model`, "Not Enough Info Found")
  )

# Flag missing job titles
qal_clean <- qal_clean |>
  mutate(title_missing = if_else(is.na(`contact/lead title`), 1L, 0L))

# Group dates for later time-based analysis
qal_clean <- qal_clean |>
  mutate(
    cohort_year    = year(`qal cohort date`),
    cohort_quarter = quarter(`qal cohort date`),
    cohort_month   = month(`qal cohort date`)
  )
```

## Target Variable Overview
```{r}
# Conversion rates overall
qal_clean |>
  summarise(
    total       = n(),
    conversions = sum(progressed),
    conv_rate   = mean(progressed)
  )

# Conversion rates by product
qal_clean |>
  group_by(solution_rollup) |>
  summarise(
    total       = n(),
    conversions = sum(progressed),
    conv_rate   = mean(progressed)
  )

# Distribution
qal_clean |>
  count(next_stage__c) |>
  mutate(pct = n / sum(n)) |>
  arrange(desc(n))
```
```{r}
# Overall conversion rates by product (barchart)
qal_clean |>
  group_by(solution_rollup) |>
  summarise(conv_rate = mean(progressed)) |>
  ggplot(aes(x = solution_rollup, y = conv_rate, fill = solution_rollup)) +
  geom_col(width = 0.5) +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            vjust = -0.5, size = 4) +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 0.25)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  labs(
    title = "Lead Conversion Rate by Product Line",
    x     = "Product",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
```{r}
# Distribution of all raw next_stage__c outcomes
qal_clean |>
  count(next_stage__c) |>
  mutate(
    pct          = n / sum(n),
    next_stage__c = fct_reorder(next_stage__c, n, .desc = TRUE)
  ) |>
  ggplot(aes(x = next_stage__c, y = n, fill = next_stage__c %in% c("SQL", "SQO", "Won"))) +
  geom_col() +
  geom_text(aes(label = scales::percent(pct, accuracy = 0.1)),
            vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = c("TRUE" = "#2166ac", "FALSE" = "#b2b2b2"),
                    labels = c("Not Progressed", "Progressed")) +
  labs(
    title = "Distribution of Lead Outcomes",
    x     = "Outcome Stage",
    y     = "Number of Leads",
    fill  = NULL
  ) +
  theme_minimal()
```
## Account-Level Analysis
```{r}
# Conversion rate by industry and product
qal_clean |>
  filter(!is.na(`acct target industry`), `acct target industry` != "Unknown") |>
  group_by(solution_rollup, `acct target industry`) |>
  summarise(
    total       = n(),
    conversions = sum(progressed),
    conv_rate   = mean(progressed),
    .groups     = "drop"
  ) |>
  arrange(solution_rollup, desc(conv_rate))
```
```{r}
# Lead distribution by industry and product
qal_clean |>
  filter(!is.na(`acct target industry`), `acct target industry` != "Unknown") |>
  group_by(solution_rollup, `acct target industry`) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(solution_rollup) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = fct_reorder(`acct target industry`, n), y = pct, fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(pct, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.55)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Lead Volume Distribution by Industry and Product",
    x     = "Industry",
    y     = "Share of Leads",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Conversion rate by industry and product
qal_clean |>
  filter(!is.na(`acct target industry`), `acct target industry` != "Unknown") |>
  group_by(solution_rollup, `acct target industry`) |>
  summarise(conv_rate = mean(progressed), .groups = "drop") |>
  ggplot(aes(x = fct_reorder(`acct target industry`, conv_rate), 
             y = conv_rate, 
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.55)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Industry and Product",
    x     = "Industry",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Conversion rate by manufacturing model and product. Filtering for models with at least 50 leads
qal_clean |>
  filter(!is.na(`acct manufacturing model`)) |>
  group_by(solution_rollup, `acct manufacturing model`) |>
  summarise(
    total       = n(),
    conversions = sum(progressed),
    conv_rate   = mean(progressed),
    .groups     = "drop"
  ) |>
  filter(total >= 50) |>
  arrange(solution_rollup, desc(conv_rate))
```

```{r}
# Conversion rate by manufacturing model (Mx)
qal_clean |>
  filter(!is.na(`acct manufacturing model`), solution_rollup == "Mx") |>
  group_by(`acct manufacturing model`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  ggplot(aes(x = fct_reorder(`acct manufacturing model`, conv_rate),
             y = conv_rate)) +
  geom_col(fill = "#2166ac") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.30)) +
  coord_flip() +
  labs(
    title = "Mx Conversion Rate by Manufacturing Model",
    x     = "Manufacturing Model",
    y     = "Conversion Rate"
  ) +
  theme_minimal()
```
```{r}
# Mx vs Qx by manufacturing model comparison
qal_clean |>
  filter(!is.na(`acct manufacturing model`)) |>
  group_by(solution_rollup, `acct manufacturing model`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 50) |>
  ggplot(aes(x = fct_reorder(`acct manufacturing model`, conv_rate),
             y = conv_rate,
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.60)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Manufacturing Model and Product",
    x     = "Manufacturing Model",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Find top site function categories by volume
qal_clean |>
  filter(!is.na(`acct primary site function`)) |>
  count(`acct primary site function`) |>
  arrange(desc(n)) |>
  head(20)
```

```{r}
# Top 15 Mx conversion rate by site function
qal_clean |>
  filter(!is.na(`acct primary site function`), solution_rollup == "Mx") |>
  group_by(`acct primary site function`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 20) |>
  slice_max(order_by = total, n = 15) |>
  ggplot(aes(x = fct_reorder(`acct primary site function`, conv_rate),
             y = conv_rate)) +
  geom_col(fill = "#2166ac") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.40)) +
  coord_flip() +
  labs(
    title = "Mx Conversion Rate by Site Function (Top 15 by Volume)",
    x     = "Site Function",
    y     = "Conversion Rate"
  ) +
  theme_minimal()
```
```{r}
# Group site functions into buckets
qal_clean <- qal_clean |>
  mutate(
    site_function_group = case_when(
      `acct primary site function` %in% c(
        "Oral solid dosage (OSD)", "Sterile injectables", "Small-molecule API",
        "Biologic API", "Cell therapies (CAR-T, NK)", "Generics manufacturing",
        "Lyophilization", "Controlled substance manufacturing"
      ) ~ "Active Pharma Manufacturing",
      `acct primary site function` %in% c(
        "Implantable devices", "In-vitro diagnostic (IVD) kits",
        "Diagnostic Equipment", "Surgical instruments", "Single-use disposables",
        "Lab Instruments"
      ) ~ "Medical Device Manufacturing",
      `acct primary site function` %in% c(
        "Non-manufacturing organization", "Drug discovery & development",
        "Clinical trials management"
      ) ~ "Non-Manufacturing",
      `acct primary site function` %in% c(
        "Food and beverage", "Nutraceutical manufacturing",
        "Cosmetics manufacturing", "Specialty Chemical Manufacturing",
        "Secondary packaging", "Consumer goods manufacturing"
      ) ~ "Other Manufacturing",
      is.na(`acct primary site function`) ~ NA_character_,
      TRUE ~ "Other / Uncategorized"
    )
  )

# Conversion rate by site function group and product
qal_clean |>
  filter(!is.na(site_function_group)) |>
  group_by(solution_rollup, site_function_group) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  arrange(solution_rollup, desc(conv_rate))
```
```{r}
# Grouped site function conversion rates by product
qal_clean |>
  filter(!is.na(site_function_group)) |>
  group_by(solution_rollup, site_function_group) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  ggplot(aes(x = fct_reorder(site_function_group, conv_rate),
             y = conv_rate,
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.40)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Site Function Group and Product",
    x     = "Site Function Group",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Conversion rate by tier and product
qal_clean |>
  filter(!is.na(`acct tier rollup`), `acct tier rollup` != "Other") |>
  group_by(solution_rollup, `acct tier rollup`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  arrange(solution_rollup, desc(conv_rate))
```

```{r}
# Conversion rate by company size and product
qal_clean |>
  filter(!is.na(`acct tier rollup`), `acct tier rollup` != "Other") |>
  group_by(solution_rollup, `acct tier rollup`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  mutate(`acct tier rollup` = factor(`acct tier rollup`,
                                     levels = c("Small", "Medium", "Large"))) |>
  ggplot(aes(x = `acct tier rollup`, y = conv_rate, fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3.5) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.30)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  labs(
    title = "Conversion Rate by Company Size and Product",
    x     = "Company Size",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Geographic Region
# Summary table
qal_clean |>
  filter(!is.na(`acct territory rollup`), `acct territory rollup` != "Unknown") |>
  group_by(solution_rollup, `acct territory rollup`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  arrange(solution_rollup, desc(conv_rate))
```
```{r}
# Visualization
qal_clean |>
  filter(!is.na(`acct territory rollup`), `acct territory rollup` != "Unknown") |>
  group_by(solution_rollup, `acct territory rollup`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  ggplot(aes(x = fct_reorder(`acct territory rollup`, conv_rate),
             y = conv_rate,
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.30)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Geographic Region and Product",
    x     = "Region",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Conversion rate by priority and product
qal_clean |>
  group_by(solution_rollup, Priority) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  arrange(solution_rollup, desc(conv_rate))
```

```{r}
# Visualize
qal_clean |>
  group_by(solution_rollup, Priority) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  ggplot(aes(x = fct_reorder(Priority, conv_rate),
             y = conv_rate,
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.70)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Lead Priority and Product",
    x     = "Priority",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Conversion rate by channel and product
qal_clean |>
  group_by(solution_rollup, `last tactic campaign channel`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  arrange(solution_rollup, desc(conv_rate))
```
```{r}
# Conversion rate by channel and product
qal_clean |>
  group_by(solution_rollup, `last tactic campaign channel`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  arrange(solution_rollup, desc(conv_rate))
```
```{r}
# Visualize
qal_clean |>
  group_by(solution_rollup, `last tactic campaign channel`) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  ggplot(aes(x = fct_reorder(`last tactic campaign channel`, conv_rate),
             y = conv_rate,
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.40)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Marketing Channel and Product",
    x     = "Channel",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
# Feature Engineering for Titles

```{r}
# Engineer seniority and functional area features from free-text job titles
qal_clean <- qal_clean |>
  mutate(
    title_lower = str_to_lower(`contact/lead title`),
    
    # Seniority classification (order matters - more specific first)
    seniority = case_when(
      is.na(title_lower) ~ "Unknown",
      str_detect(title_lower, "\\bceo\\b|\\bcoo\\b|\\bcfo\\b|\\bcto\\b|\\bcqo\\b|\\bchief\\b|\\bpresident\\b|\\bowner\\b|\\bfounder\\b") ~ "C-Level",
      str_detect(title_lower, "\\bvp\\b|\\bvice president\\b") ~ "VP",
      str_detect(title_lower, "\\bdirector\\b") ~ "Director",
      str_detect(title_lower, "\\bmanager\\b|\\bmanagement\\b") ~ "Manager",
      str_detect(title_lower, "\\bsenior\\b|\\bsr\\.?\\b|\\blead\\b|\\bprincipal\\b") ~ "Senior Individual Contributor",
      str_detect(title_lower, "\\bengineer\\b|\\bscientist\\b|\\banalyst\\b|\\bspecialist\\b|\\bcoordinator\\b|\\bconsultant\\b|\\bassociate\\b") ~ "Individual Contributor",
      TRUE ~ "Other"
    ),
    
    # Functional area flags (not mutually exclusive)
    func_quality      = if_else(str_detect(title_lower, "quality|qa\\b|qc\\b|qms|compliance|assurance"), 1L, 0L, missing = 0L),
    func_regulatory   = if_else(str_detect(title_lower, "regulat|ra\\b|affairs|submission"), 1L, 0L, missing = 0L),
    func_manufacturing = if_else(str_detect(title_lower, "manufactur|production|process|plant|operations|supply chain|supply\\b"), 1L, 0L, missing = 0L),
    func_rd           = if_else(str_detect(title_lower, "research|r&d|development|scientific|science|clinical"), 1L, 0L, missing = 0L),
    func_it           = if_else(str_detect(title_lower, "\\bit\\b|information tech|systems|software|digital|data|eqms|erp"), 1L, 0L, missing = 0L),
    
    # Primary functional area (mutually exclusive, priority order)
    func_area = case_when(
      is.na(title_lower)                                          ~ "Unknown",
      func_manufacturing == 1 & func_quality == 0                ~ "Operations/Manufacturing",
      func_quality == 1 & func_regulatory == 1                   ~ "Quality & Regulatory",
      func_quality == 1                                          ~ "Quality",
      func_regulatory == 1                                       ~ "Regulatory",
      func_it == 1                                               ~ "IT/Systems",
      func_rd == 1                                               ~ "R&D",
      func_manufacturing == 1                                    ~ "Operations/Manufacturing",
      TRUE                                                       ~ "Other/Unknown"
    )
  )
```

```{r}
# Seniority level distribution
qal_clean |>
  count(seniority) |>
  mutate(pct = n / sum(n)) |>
  arrange(desc(n))
```
```{r}
# Conversion rate by seniority and product
qal_clean |>
  filter(seniority != "Unknown") |>
  group_by(solution_rollup, seniority) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  mutate(seniority = factor(seniority, levels = c(
    "C-Level", "VP", "Director", "Manager",
    "Senior Individual Contributor", "Individual Contributor", "Other"
  ))) |>
  ggplot(aes(x = seniority, y = conv_rate, fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.40)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  labs(
    title = "Conversion Rate by Seniority Level and Product",
    x     = "Seniority Level",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```
```{r}
# Conversion rate by functional area and product
qal_clean |>
  filter(func_area != "Unknown") |>
  group_by(solution_rollup, func_area) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 30) |>
  ggplot(aes(x = fct_reorder(func_area, conv_rate),
             y = conv_rate,
             fill = solution_rollup)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.45)) +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  coord_flip() +
  labs(
    title = "Conversion Rate by Functional Area and Product",
    x     = "Functional Area",
    y     = "Conversion Rate",
    fill  = "Product"
  ) +
  theme_minimal()
```
```{r}
# Heatmap: Seniority x Functional area for Mx conversion rates
qal_clean |>
  filter(solution_rollup == "Mx",
         seniority != "Unknown",
         seniority != "Other",
         func_area != "Unknown",
         func_area != "Other/Unknown") |>
  group_by(seniority, func_area) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 15) |>
  mutate(seniority = factor(seniority, levels = c(
    "C-Level", "VP", "Director", "Manager",
    "Senior Individual Contributor", "Individual Contributor"
  ))) |>
  ggplot(aes(x = func_area, y = seniority, fill = conv_rate)) +
  geom_tile(color = "white") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 1)),
            size = 3) +
  scale_fill_gradient(low = "#deebf7", high = "#08306b",
                      labels = scales::percent_format()) +
  labs(
    title = "Mx Conversion Rate: Seniority × Functional Area",
    x     = "Functional Area",
    y     = "Seniority Level",
    fill  = "Conv. Rate"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
```
```{r}
# Missing title conversions
qal_clean |>
  group_by(solution_rollup, title_missing) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  mutate(title_missing = if_else(title_missing == 1, "Title Missing", "Title Present"))
```
```{r}
# Conversion rate by year and product
qal_clean |>
  group_by(solution_rollup, cohort_year) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  )
```
```{r}
# Conversion rate by quarter and product
qal_clean |>
  mutate(year_quarter = paste0(cohort_year, " Q", cohort_quarter)) |>
  group_by(solution_rollup, year_quarter) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  ggplot(aes(x = year_quarter, y = conv_rate, color = solution_rollup, group = solution_rollup)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2.5) +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 0.1)),
            vjust = -0.8, size = 3) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.30)) +
  scale_color_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  labs(
    title = "Conversion Rate by Quarter and Product",
    x     = "Quarter",
    y     = "Conversion Rate",
    color = "Product"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
```{r}
# Lead volume by quarter and product (to check if volume shifts explain rate changes)
qal_clean |>
  mutate(year_quarter = paste0(cohort_year, " Q", cohort_quarter)) |>
  group_by(solution_rollup, year_quarter) |>
  summarise(total = n(), .groups = "drop") |>
  ggplot(aes(x = year_quarter, y = total, fill = solution_rollup)) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = c("Mx" = "#2166ac", "Qx" = "#d73027")) +
  labs(
    title = "Lead Volume by Quarter and Product",
    x     = "Quarter",
    y     = "Number of Leads",
    fill  = "Product"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```
```{r}
# Industries that convert above their respective product baselines for both Mx and Qx
mx_baseline <- qal_clean |> filter(solution_rollup == "Mx") |> summarise(r = mean(progressed)) |> pull(r)
qx_baseline <- qal_clean |> filter(solution_rollup == "Qx") |> summarise(r = mean(progressed)) |> pull(r)

qal_clean |>
  filter(!is.na(`acct target industry`), `acct target industry` != "Unknown") |>
  group_by(`acct target industry`, solution_rollup) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  pivot_wider(names_from = solution_rollup, values_from = c(total, conv_rate)) |>
  mutate(
    above_mx_baseline = conv_rate_Mx > mx_baseline,
    above_qx_baseline = conv_rate_Qx > qx_baseline,
    cross_sell        = above_mx_baseline & above_qx_baseline
  ) |>
  arrange(desc(cross_sell), desc(conv_rate_Mx))
```
```{r}
# Scatter plot: Mx vs Qx conversion rate by industry (cross-sell quadrant view)
qal_clean |>
  filter(!is.na(`acct target industry`), `acct target industry` != "Unknown") |>
  group_by(`acct target industry`, solution_rollup) |>
  summarise(conv_rate = mean(progressed), total = n(), .groups = "drop") |>
  pivot_wider(names_from = solution_rollup, values_from = c(conv_rate, total)) |>
  ggplot(aes(x = conv_rate_Qx, y = conv_rate_Mx, label = `acct target industry`)) +
  geom_point(aes(size = total_Mx), color = "#2166ac", alpha = 0.7) +
  geom_text(vjust = -0.8, size = 3.5) +
  geom_vline(xintercept = qx_baseline, linetype = "dashed", color = "#d73027", alpha = 0.6) +
  geom_hline(yintercept = mx_baseline, linetype = "dashed", color = "#2166ac", alpha = 0.6) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0.08, 0.30)) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0.08, 0.22)) +
  labs(
    title = "Cross-Sell Quadrant: Mx vs Qx Conversion Rate by Industry",
    subtitle = "Dashed lines = product baselines. Top-right quadrant = cross-sell opportunities",
    x     = "Qx Conversion Rate",
    y     = "Mx Conversion Rate",
    size  = "Mx Lead Volume"
  ) +
  theme_minimal()
```
```{r}
# Same quadrant view by manufacturing model
qal_clean |>
  filter(!is.na(`acct manufacturing model`)) |>
  group_by(`acct manufacturing model`, solution_rollup) |>
  summarise(conv_rate = mean(progressed), total = n(), .groups = "drop") |>
  filter(total >= 50) |>
  pivot_wider(names_from = solution_rollup, values_from = c(conv_rate, total)) |>
  filter(!is.na(conv_rate_Mx), !is.na(conv_rate_Qx)) |>
  ggplot(aes(x = conv_rate_Qx, y = conv_rate_Mx, label = `acct manufacturing model`)) +
  geom_point(aes(size = total_Mx), color = "#2166ac", alpha = 0.7) +
  geom_text(vjust = -0.8, size = 3) +
  geom_vline(xintercept = qx_baseline, linetype = "dashed", color = "#d73027", alpha = 0.6) +
  geom_hline(yintercept = mx_baseline, linetype = "dashed", color = "#2166ac", alpha = 0.6) +
  scale_x_continuous(labels = scales::percent_format()) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Cross-Sell Quadrant: Mx vs Qx Conversion Rate by Manufacturing Model",
    subtitle = "Top-right quadrant = strong cross-sell candidates",
    x     = "Qx Conversion Rate",
    y     = "Mx Conversion Rate",
    size  = "Mx Lead Volume"
  ) +
  theme_minimal()
```
```{r}
# Top Mx-converting industry x seniority combinations (min 20 leads)
qal_clean |>
  filter(
    solution_rollup == "Mx",
    !is.na(`acct target industry`),
    `acct target industry` != "Unknown",
    seniority != "Unknown",
    seniority != "Other"
  ) |>
  group_by(`acct target industry`, seniority) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 20) |>
  arrange(desc(conv_rate)) |>
  head(15)
```

```{r}
# Heatmap: Industry x Seniority for Mx
qal_clean |>
  filter(
    solution_rollup == "Mx",
    !is.na(`acct target industry`),
    `acct target industry` != "Unknown",
    seniority != "Unknown",
    seniority != "Other"
  ) |>
  group_by(`acct target industry`, seniority) |>
  summarise(
    total     = n(),
    conv_rate = mean(progressed),
    .groups   = "drop"
  ) |>
  filter(total >= 15) |>
  mutate(seniority = factor(seniority, levels = c(
    "C-Level", "VP", "Director", "Manager",
    "Senior Individual Contributor", "Individual Contributor"
  ))) |>
  ggplot(aes(x = `acct target industry`, y = seniority, fill = conv_rate)) +
  geom_tile(color = "white") +
  geom_text(aes(label = scales::percent(conv_rate, accuracy = 1)), size = 3) +
  scale_fill_gradient(low = "#deebf7", high = "#08306b",
                      labels = scales::percent_format()) +
  labs(
    title = "Mx Conversion Rate: Industry × Seniority",
    x     = "Industry",
    y     = "Seniority Level",
    fill  = "Conv. Rate"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```
```{r}
# Quick summary table of key Mx findings for the results section
tibble::tribble(
  ~Dimension,              ~Best_for_Mx,                        ~Mx_Conv_Rate,
  "Industry",              "Blood & Biologics",                 "18.0%",
  "Industry",              "Medical Device",                    "15.9%",
  "Manufacturing Model",   "CMO",                               "24.9%",
  "Manufacturing Model",   "CDMO",                              "17.8%",
  "Site Function Group",   "Other Manufacturing",               "33.8%",
  "Site Function Group",   "Medical Device Manufacturing",      "19.1%",
  "Company Size",          "Small",                             "16.8%",
  "Region",                "Japan",                             "24.0%",
  "Region",                "Americas",                          "15.0%",
  "Seniority",             "C-Level",                           "21.2%",
  "Functional Area",       "Quality & Regulatory",              "17.8%",
  "Lead Priority",         "P1 - Video Demo",                   "32.5%",
  "Lead Priority",         "P1 - Contact Us",                   "30.6%",
  "Channel",               "SEO",                               "27.0%",
  "Channel",               "Direct/Inbound",                    "24.3%"
)
```

